Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-07-26 ms.tex
further typo corrections in the description of the HDS spectra.

\clearpage
\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec.pdf}
\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
There are many bad pixels, which are preliminarily discarded for fluxes above 1.25.
These are not fully removed in the convolved spectrum.}\label{fig:naDlines}
\end{centering}
\end{figure}

@@

\begin{deluxetable*}{lcrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}\label{tab:stellObsParams}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}
\end{deluxetable*}

@@

\subsection{Observations}

@@

In one independent analysis (E Schlawin), we we follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD separately.
Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.

The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/ume/node16.html}) has a sharper PSF and and is easier to trace.
The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
For wavelength identification, a Thorium Argon reference is used.
(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).

>>>>

\clearpage

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Na_D_spec.pdf}
\caption{{\it Top:} Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
There are many bad pixels, which are preliminarily discarded for fluxes above 1.25.
{\it Bottom:} The measured spectrum is convolved with a Gaussian kernel to match the resolution of the HIGHRES models which are calculated for log(g)=4.5 and 4.0.
The measured Na D$_1$ and D$_2$ lines are deeper than either model, but have similar line ratios to the 4500 K log(g)=4.5 model.}\label{fig:naDlines}
\end{centering}
\end{figure}

@@

\begin{deluxetable*}{lcrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
\end{deluxetable*}

@@

\subsection{Subaru HDS Spectra}

@@

In one independent analysis (E Schlawin), we we follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.

The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm, R=50,000\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/ume/node16.html}) has a sharper PSF and and is easier to trace.
The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
The \texttt{iraf} tracing routines fail with the image slicer, so we use a a flat field with a narrower (0.3 mm) slit to create traces for the 2013 data with the image slicer.
For wavelength identification, a Thorium Argon reference is used.
(Note to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined near some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines}), the Mg Triplet (Figure \ref{fig:mgTriplet}) and the Ca I 6262 $\AA$ line (Figure \ref{fig:CaILine}).
